---
title: "ENV S 193DS - Homework 3"
author: "Andrew Liang"
date: now
format: pdf
editor: visual
toc: true 
warning: false 
message: false 
---

## Link to Forked Repository: https://github.com/andrewjliang/liang_andrew-homework-03

# Setup

```{r}
rm(list = ls())
getwd()

library(tidyverse)
library(readxl)
library(here)
library(janitor)
library(GGally)
library(MuMIn)
library(ggeffects)
library(gtsummary)
library(flextable)
library(modelsummary)

drought_exp <- read_xlsx(path = here("data", 
                                     "Valliere_etal_EcoApps_Data.xlsx"),
                         sheet = "First Harvest")

drought_exp_clean <- drought_exp %>% 
  clean_names() %>% # nicer column names
  mutate(species_name = case_when( # adding column with species scientific names
    species == "ENCCAL" ~ "Encelia californica", # bush sunflower
    species == "ESCCAL" ~ "Eschscholzia californica", # California poppy
    species == "PENCEN" ~ "Penstemon centranthifolius", # Scarlet bugler
    species == "GRICAM" ~ "Grindelia camporum", # great valley gumweed
    species == "SALLEU" ~ "Salvia leucophylla", # Purple sage
    species == "STIPUL" ~ "Nasella pulchra", # Purple needlegrass
    species == "LOTSCO" ~ "Acmispon glaber" # deerweed
  )) %>% 
  relocate(species_name, .after = species) %>% # moving species_name column after species
  mutate(water_treatment = case_when( # adding column with full treatment names
    water == "WW" ~ "Well-Watered",
    water == "DS" ~ "Drought-Stressed"
  )) %>% 
  relocate(water_treatment, .after = water) # moving water_treatment column after water
```

# Problem 1. Multiple Linear Regression: Model Selection and Construction

## a. Table

```{r}
model0 <- lm(total_g ~ 1, # formula
             data = drought_exp_clean) # data frame
model1 <- lm(total_g ~ sla + water_treatment + species_name,
             data = drought_exp_clean)
model2 <- lm(total_g ~ sla + water_treatment,
             data = drought_exp_clean)
model3 <- lm(total_g ~ sla + species_name,
             data = drought_exp_clean)
model4 <- lm(total_g ~ water_treatment + species_name, drought_exp_clean)

modelsummary::modelsummary( # this function takes a list of models
  list( 
    "null" = model0, # "model name" = model object
    "model 1" = model1,
    "model 2" = model2,
    "model 3" = model3,
    "model 4" = model4
  )
) 
```

## b. 

## c.

## d.

## e.

# Problem 2 - Affective Visualization

## a.

*My thought for an affective visualization for my data would include some sort of reference to sleep or trying to get on the bus. Many stories often include images of a student missing the bus to school, which I believe could easily be replicated for this project. The main reason I may have trouble getting on the bus is oversleeping or taking too long to prepare for the day.*

## b. 

## c.

## d.

*The Sleeping Man*

*College students often struggle to wake up on time to catch the bus, especially for classes at 8:00 or 9:00 AM. Similarly, a lot of people take the bus to and from school, but find that they may miss the bus by a mere minute because they take too long to prepare for the day or even because the bus arrives a few minutes earlier than usual.*

# Problem 3 - Statistical Critique

## a.

## b. 

## c.

## d.
